---
title: "lab5-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab5-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(APIpkg)
```

# Description

Musical taste comparator between different countries using Spotify's data.
\newline
\newline

# Usage
```R
install.packages("devtools")
devtools::install_github("mapama247/732A94lab5")
```
# Functions

## compare_countries( countries_list )

### Input
Takes as input a list of several 2-letter country codes. List of available countries:

* Argentina,AR
* Australia,AU
* Austria,AT
* Belgium,BE
* Bolivia,BO
* Brazil,BR
* Bulgaria,BG
* Canada,CA
* Czech Republic,CZ
* Chile,CL
* Colombia,CO
* Costa Rica,CR
* Dinamarca,DK
* Dominican Republic,DO
* Ecuador,EC
* El Salvador,SV
* Estonia,EE
* Finland,FI
* France,FR
* Germany,DE
* Greece,GR
* Guatemala,GT
* Honduras,HN
* Hong Kong,HK
* Hungary,HU
* India,IN
* Indonesia,ID
* Ireland,IE
* Iceland,IS
* Israel,IL
* Italy,IT
* Japan,JP
* Latvia,LV
* Lithuania,LT
* Luxembourg,LU
* Malaysia,MY
* Malta,MT
* Mexico,MX
* Netherlands,NL
* Nicaragua,NI
* Norway,NO
* New Zeland,NZ
* Panama,PA
* Paraguay,PY
* Peru,PE
* Philippines,PH
* Poland,PL
* Portugal,PT
* Romania,RO
* Slovakia,SK
* Spain,ES
* Singapore,SG
* South Africa,ZA
* Sweden,SE
* Switzerland,SW
* Thailand,TH
* Taiwan,TW
* Turkey,TK
* United Kingdom,UK
* Uruguay,UY
* United States,US
* Vietnam,VN

### Output
Returns a data.frame with the following features averaged over all songs in each countrie's playlist:

* code
* followers
* explicit
* danceability
* energy
* key
* loudness
* mode
* speechiness
* acousticness
* instrumentalness
* liveness
* valence
* tempo

## Resource

Check the [Spotify API website](https://developer.spotify.com/documentation/web-api/) for further information.



## Examples
```R
countries <- list("ES","PT")
spain_vs_portugal <- playlists_comparator(countries)

comparison_all_countries <- playlists_comparator()
```
